### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Edits to uncertainty discussion

The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure. Based on the goals of the analysis and the information collected, several engineering approximations were made. For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known. The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations. The HRR of the fire was estimated using documentation of the potential fuel load within the structure. Although there might be differences between the actual values and those used in the simulation, the model input parameters represent our best estimate of the fire scenario based on the information that was available. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.

>>>>

The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure. Based on the goals of the analysis and the information collected, several engineering approximations were made. For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known. The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations. The HRR of the fire was estimated using documentation of the potential fuel load within the structure.

In reality, the quantities associated with these input parameters are not fixed values; rather, the model input parameters can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty. Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature). For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power. Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}. More detailed discussion on the propagation of parameter uncertainty in fire models is available in NUREG-1824 Supplement~1~\cite{NUREG_1824_Sup_1}. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
